Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2024-01-24 doc/paper.tex
Updape paper
Signed-off-by: Jonatan Hanssen <jonatan.hanssen@outlook.com>

We select three different Minigrid environments with increasing complexity; Empty, DoorKey and UnlockPickup. For each environment we test our four different models; PPO with no LLM integration, PPO with LLM reward shaping, PPO with LLM policy influencing and PPO with both reward shaping and policy influencing (A2C2). All methods use the same hyperparameters for the PPO, which can be found in the appendix. For each of these methods, we run PPO for 2000 (200 for Empty) episodes of 1024 steps, and track the reward\footnote{The true environment reward, not including pseudo-rewards given by the LLM in reward shaping} received for each one. We do this eight times per method, and compare the average results per episode against each other.

@@

Regardless of these shortcomings in the performance of policy influencing, it seems to have contributed positively when combining the two methods in A2C2, which outperformed each of the methods in both the Empty and DoorKey environments. As mentioned in Section \ref{emptyresultstext}, it seems that because the reward shaping makes the PPO learn the environment faster, it lessens the conflict between the influences of the LLM and the PPO itself on the logits. This allows the PPO to exert the most influence on the logits earlier on. However, this conflict is not entirely negated, as witnessed in the UnlockPickup environment where reward shaping still vastly outperforms both policy influencing and A2C2.

>>>>

We select three different Minigrid environments with increasing complexity; Empty, DoorKey and UnlockPickup. For each environment we test our four different models; PPO with no LLM integration, PPO with LLM reward shaping, PPO with LLM policy influencing and PPO with both reward shaping and policy influencing (A2C2). All methods use the same hyperparameters for the PPO, which can be found in the \nameref{sec:appendixtext}. For each of these methods, we run PPO for 2000 (200 for Empty) episodes of 1024 steps, and track the reward\footnote{The true environment reward, not including pseudo-rewards given by the LLM in reward shaping} received for each one. We do this eight times per method, and compare the average results per episode against each other.

@@

Regardless of these shortcomings in the performance of policy influencing, it seems to have contributed positively when combining the two methods in A2C2, which outperformed each of the methods in both the Empty and DoorKey environments. As mentioned in Section \ref{emptyresultstext}, it seems that because the reward shaping makes the PPO learn the environment faster, it lessens the conflict between the influences of the LLM and the PPO itself on the logits. This allows the PPO to exert the most influence on the logits earlier on. However, this conflict is not entirely negated, as witnessed in the UnlockPickup environment where reward shaping still outperforms both policy influencing and A2C2.
